---
title: Cleanup Score Extractions
output: html_document
---


```{r}
library(XLConnect)
library(stringr)
```

Read the Excel file (from copy initially)
Connect to local MySQL server and read scores from tracking file.

```{r}
library(RMySQL)
con = dbConnect(MySQL(), dbname='appy')
dbListTables(con)
dbWriteTable(con,"trackingFile",mergedPubmedTracking,overwrite=T)

# a function to simplify queries

query <- function(...) dbGetQuery(con, ...) 

# all with any score
pmid_scores_tracking <- query("SELECt PMID FROM trackingfile WHERE include_ = 'yes' AND test_performance = 'yes' 
                               AND test_type LIKE '%score%'")
pmid_score_tracking <- pmid_scores_tracking$PMID
pmid_score_tracking
```


```{r}
## NB list sheets: http://stackoverflow.com/questions/12945687/how-to-read-all-worksheets-in-an-excel-workbook-into-an-r-list-with-data-frame-e

wb <-loadWorkbook("C:/Users/dsteele/Desktop/scores_extraction_6-23-2014.xlsx")
score_extracts  <- readWorksheet(wb, sheet=getSheets(wb)[1])
pmid_score_extracts <- score_extracts$study_pmid
pmid_score_extracted_papers <- as.numeric(unique(score_extracts$study_pmid))
pmid_score_extracted_papers
pmid_score_extracted_papers[c(72,73)]

```

The scores file has been read into an R data.frame 'scores_extracts' from the local copy

How many unique papers are there which have extracted scores?
Which papers have been extracted, but are not indicated as such in tracking file?

```{r}

setdiff(pmid_score_extracted_papers, pmid_score_tracking)
setdiff(pmid_score_tracking, pmid_score_extracted_papers)


```

Which papers containing 'score' have include_ = 'no?' OR test_performance='no'
```{r}
(pmid_scores_out <- query("SELECt PMID FROM trackingfile WHERE include_ = 'no?' AND test_type LIKE '%score%'"))
(pmid_scores_noTP  <- query("SELECt PMID FROM trackingfile WHERE test_performance = 'no?' 
                           AND test_type LIKE '%score%'"))

```

```{r}
## TODO: regular expressions to clean extraction file
cutpoints <- str_replace(scores$definition_of_a_positive_test, ">=", "")
cutpoints <- str_trim(cutpoints, side = "both")

## TODO: replace multiple patterns using "|"?
cutpoints <- str_replace_all(scores$definition_of_a_positive_test, "[a-zA-Z]| >= | \\.", "")

write.csv(cbind(scores$definition_of_a_positive_test, cutpoints), file="scoresTest.csv")
```





