---
title: Cleanup Score Extractions
output: html_document
---


```{r}
library(XLConnect)
library(stringr)
```

Connect to local MySQL server and read scores from tracking file.
Read the Excel file (from dropbox copy)

```{r}
library(RMySQL)
con = dbConnect(MySQL(), dbname='appy')
dbListTables(con)
dbWriteTable(con,"trackingFile",mergedPubmedTracking,overwrite=T)

# a function to simplify queries

query <- function(...) dbGetQuery(con, ...) 

# all with any score
pmid_scores_tracking <- query("SELECt PMID FROM trackingfile WHERE include_ = 'yes' AND test_performance = 'yes' 
                               AND test_type LIKE '%score%'")
pmid_score_tracking <- pmid_scores_tracking$PMID
pmid_score_tracking
```

Read the scores_extraction worksheet into R (from Dropbox copy)

```{r}
## NB list sheets: http://stackoverflow.com/questions/12945687/how-to-read-all-worksheets-in-an-excel-workbook-into-an-r-list-with-data-frame-e

wb <- loadWorkbook("D:/Dropbox/BrownCEBM/Appendicitis/scores_extraction_6-23-2014.xlsx")
scoredat  <- readWorksheet(wb, sheet=getSheets(wb)[1])
pmid_score_extracts <- scoredat$study_pmid
pmid_score_extracted_papers <- as.numeric(unique(scoredat$study_pmid))

names(scoredat)
scoredat$source_pmid[scoredat$test == 'Ramirez']
```

How many unique papers are there which have extracted scores?
Which papers have been extracted, but are not indicated as such in tracking file?

```{r}

setdiff(pmid_score_extracted_papers, pmid_score_tracking)
setdiff(pmid_score_tracking, pmid_score_extracted_papers)


```

Which papers containing 'score' have include_ = 'no?' OR test_performance='no'

```{r}
(pmid_scores_out <- query("SELECt PMID FROM trackingfile WHERE include_ = 'no?' AND test_type LIKE '%score%'"))
(pmid_scores_noTP  <- query("SELECt PMID FROM trackingfile WHERE test_performance = 'no?' 
                           AND test_type LIKE '%score%'"))

```

Use regular expressions to clean, harmonize and create dummy variables for analysis.


```{r}
wb <- loadWorkbook("D:/Dropbox/BrownCEBM/Appendicitis/scores_extraction_6-23-2014.xlsx")
scoredat  <- readWorksheet(wb, sheet=getSheets(wb)[1])
names(scoredat)
library(stringr)
cutPoint <- str_trim(str_replace(str_replace(scoredat$definition_of_a_positive_test, ">=", ""),
                                 "score", ""), side="both")

scoreName <- str_trim(str_replace(scoredat$test, "score|scoring system", ""), side="both")
scoreName

table(scoredat$Population)
```





